%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape YuJia Liang} \\ \vspace{1pt}
    \small +886 965 160 695 $|$ \href{mailto:ch993115@gmail.com}{\underline{ch993115@gmail.com}} $|$ \href{https://www.linkedin.com/in/yu-jia-liang-77ab022a7}{\underline{LinkedIn Profile}} $|$ \href{https://github.com/itsYoga}{\underline{GitHub Profile}}
    %\href{https://www.linkedin.com/in/oren-kaplan-8380b1231/}%{\underline{https://www.linkedin.com/in/oren-kaplan}} $|$
    $|$ {\small{Taipei, Taiwan}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Taiwan Ocean University}{Keelung, Taiwan}
      {B.S. in Computer Science and Engineering - GPA: 3.6/4.0} {Sep. 2022 -- Present (EST. May 2026))}\hfill \break

  \textbf{Relevant Courses}{: Data Structures, Algorithms, Operating Systems, Computer Networks, Database Systems, Digital Logic, Computer Organization, Information Security, Introduction to AI, Web Programming, Java, Python, Verilog, SwiftUI, Graph Algorithms, Discrete Mathematics} 

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
%\section{Volunteer Experience}
%  \resumeSubHeadingListStart

 %   \resumeSubheading
  %    {Research Lab Volunteer}{Nov. 2024 -- present}
   %   {Tukey Lab, UCSD}{La Jolla, CA}
    %  \resumeItemListStart
     %   \resumeItem{Conducted PCR assays to amplify DNA for analysis, ensuring accuracy in sample preparation and handling.}
      %  \resumeItem{Collected and processed tissue samples from mice, following standardized protocols for tissue preservation and documentation.}
       % \resumeItem{Assisted with routine laboratory tasks, including reagent preparation, sample labeling, and equipment maintenance, to support daily lab operations.}
       % \resumeItem{Maintained cleanliness and organization of lab areas, adhering to strict safety and quality control standards.}
      %\resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

 % \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Research \& Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Volleyball Line Judging System}{Nov. 2024 -- present}
      {OpenCV, Python | Advisor: Prof. Pei-Yi, Ding}{Team size: 3}
      \resumeItemListStart
        \resumeItem{Designed an automated in/out detection system for volleyball using OpenCV and image classification.}
        \resumeItem{Captured and processed real-time court imagery to identify ball boundaries and improve officiating accuracy.}
      \resumeItemListEnd

      \resumeSubheading
      {Archon RWA Tokenization DApp}{2025}
      {React, TypeScript, Solidity, Hardhat, Ethers.js, Tailwind CSS}{Team size: 1}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive DeFi platform for Real-World Asset (RWA) tokenization with role-based access control (ADMIN, VERIFIER, MINTER roles).}
        \resumeItem{Implemented smart contracts for identity verification, asset management, and ERC20 token creation with automated deployment and role setup.}
        \resumeItem{Built a modern React frontend with TypeScript, real-time wallet integration, and responsive design using Tailwind CSS.}
        \resumeItem{Integrated MetaMask wallet support with real-time account switching and comprehensive testing suite for all platform features.}
      \resumeItemListEnd

      \resumeSubheading
      {Image Processing Project}{2025}
      {Python, OpenCV, NumPy, scikit-image}{Team size: 1}
      \resumeItemListStart
        \resumeItem{Implemented comprehensive image processing algorithms including ISP (Image Signal Processing) pipeline and 3A (Auto Exposure, Auto Focus, Auto White Balance) algorithms.}
        \resumeItem{Developed computer vision features including edge detection, feature detection, image enhancement, noise reduction, and image segmentation.}
        \resumeItem{Created a modular architecture with efficient processing pipeline achieving sub-5-second average processing time per image.}
      \resumeItemListEnd

      \resumeSubheading
      {ASL Hand Gesture Recognition App }{Dec. 2024 -- Feb. 2025}
      {SwiftUI, CreateML}{Team size: 1}
      \resumeItemListStart
        \resumeItem{Trained a custom machine learning model to classify 28 hand gestures (A-Z, Space, Delete) using CreateML.}
        \resumeItem{Integrated real-time camera input into a SwiftUI iOS app to enable sentence construction from gestures.}
        \resumeItem{Designed a user-friendly interface for accessibility in communication.}
        \resumeItem{WWDC2025 Submission}
      \resumeItemListEnd
      \resumeSubheading
      {School Course Selection Web System}{Dec. 2024 -- Jan. 2025}
      {PHP, MySQL}{Team size: 3}
      \resumeItemListStart
        \resumeItem{Developed a role-based course selection platform with secure login and selection validation.}
        \resumeItem{Implemented admin-side class management and backend database integration.}
      \resumeItemListEnd
      \resumeSubheading
      {SyncUp - Social Calendar App}{2025}
      {Flutter, Firebase, Google Maps API}{Team size: 1}
      \resumeItemListStart
        \resumeItem{Developed a modern social calendar app with real-time event sharing and friend management using Flutter and Firebase.}
        \resumeItem{Implemented location-based event suggestions and interactive calendar interface with Google Maps integration.}
        \resumeItem{Integrated Firebase Authentication, Cloud Firestore, and real-time chat features with read receipts.}
      \resumeItemListEnd
        
            %\resumeItem{Created impactful visualizations showcasing correlations between social media activity and protest events, supporting data-driven insights.}


    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {ITRI}{Jun. 2025 -- Aug. 2025}
        {\textit{AI Image Recognition Intern, Electronics and Optoelectronics Research Laboratories}}{Hsinchu, Taiwan}
        \resumeItemListStart
          \resumeItem{Assisted in object detection model pruning, training, and deployment for embedded systems.}
          \resumeItem{Implemented image streaming and detection results transmission via Ethernet for real-time processing.}
          \resumeItem{Optimized YOLO object detection models through pruning techniques and model transplantation.}
          \resumeItem{Supported reproduction and exploration of other state-of-the-art (SOTA) models for research purposes.}
        \resumeItemListEnd
      % (keep other experiences here, if any)
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Java, Python, TypeScript, JavaScript, HTML, SQL, MATLAB, Verilog, SwiftUI, PHP} \\
     \textbf{Tools}{: Git, VS Code, Jupyter Notebook, Firebase} \\
     \textbf{Frameworks}{: React, Bootstrap} \\
     \textbf{Languages}{: English (Fluent), Mandarin (Fluent), Japanese (JLPT N3)}
    }}
 \end{itemize}

%-----------EXTRACURRICULAR ACTIVITIES-----------
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
      % Tennis Entry (uses resumeSubheading with 4 args)
      \resumeSubheading
        {National Taiwan Ocean University Tennis Team Member}{2022 - 2023}{}{Keelung, Taiwan} % Example using 4 args
      % Volleyball Entry (uses resumeSubheading with 4 args)
      \resumeSubheading
        {Volleyball Department Team Member}{2022 - 2025}{}{Keelung, Taiwan} % Example using 4 args
        % Add description if available, otherwise remove resumeItemListStart/End
      % Hackathon Entry (uses resumeSubheading with 4 args - might look odd)
      \resumeSubheading
        {Hackathon Participant}{2024}{}{} 

    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document} 